### 2023-06-25 Draft.tex
Fixed citation

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering\includegraphics[width=0.60\textwidth]{img/higher.PNG}
    \caption{Fourth-order steerable filter (a) original test pattern (b) average oriented output (c) dominant orientation (d) oriented energy as a function of angle (polar plot)}\cite{Szeliski_2022}
\end{figure}\end{minipage}

>>>>

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering\includegraphics[width=0.60\textwidth]{img/higher.PNG}
    \caption{Fourth-order steerable filter (a) original test pattern (b) average oriented output (c) dominant orientation (d) oriented energy as a function of angle (polar plot)\cite{Szeliski_2022}}
\end{figure}\end{minipage}
